When Operators Learned How to Split Up

### 2010-11-18 trunk/Papers/operator-splitting/equiv-definition-carlos.tex
fixed some bugs in carlos part

A \emph{planning domain} $D$ is a finite set of actions. \fixme{If we want, we can define something like a `\emph{restricted planning domain}' as a pair $D=\tup{A,R}$ where $A$ is a finite set of actions, and $R$ is a finite set of 
propositional formulas$.  We would use $R$ to restrict planning tasks by requesting consistency with $R$.}

A \emph{planning task} is a tuple $\tup{D, P}$
where $D$ is a planning domain and  $P=\tup{I,F)$ 
is an \emph{instance description}, consisting of a finite set of literals $I$
(the \emph{initial state}) and the a finite set of literals $O$ (the \emph{final state}).

>>>>

A \emph{planning domain} $D$ is a finite set of actions. \fixme{If we want, we can define something like a `\emph{restricted planning domain}' as a pair $D=\tup{A,R}$ where $A$ is a finite set of actions, and $R$ is a finite set of 
propositional formulas.  We would use $R$ to restrict planning tasks by requesting consistency with $R$.}

A \emph{planning task} is a tuple $\tup{D, P}$
where $D$ is a planning domain and  $P=\tup{I,F}$ 
is an \emph{instance description}, consisting of a finite set of literals $I$
(the \emph{initial state}) and the a finite set of literals $O$ (the \emph{final state}).
